---
title: "HW2_final"
author: "Chaitali Sawant,Hashita Gadiraju,Kyle Brown,Shivani Agarwal"
date: "1/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Ques4 4.	Simulate the 1R algorithm.  IGNORE RISK LEVEL A.  Build a 1R rule for each of Primary Condition Group, Charlson Index, and Length of Stay.  Which one works better?
>Results based on oneR package.

```{r}
library(OneR)
Heritage<- data.frame(Heritage_RiskADeleted)
data <- optbin(Heritage)
model<- OneR(data, verbose = TRUE)
summary(model)
prediction <- predict(model,Heritage)
eval_model(prediction,Heritage)
```

### OneRModel
### Binary tree for CharlsonIndex

```{r}

library(rpart)
library(rpart.plot)
dim(Heritage_RiskADeleted)
dtm <- rpart(RiskLevel~CharlsonIndex,Heritage_RiskADeleted,method = "class")
dtm
rpart.plot(dtm)
```

### Binary tree for LengthofStay

```{r}
library(RcppGreedySetCover)
library(printr)
library(stats)
library(rpart)
library(rpart.plot)
dim(Heritage_RiskADeleted)
dtm <- rpart(RiskLevel~LengthOfStay,Heritage_RiskADeleted,method = "class")
dtm
rpart.plot(dtm)
```

### Binary tree for PrimaryConditionGroup
```{r}
library(RcppGreedySetCover)
library(printr)
library(stats)
library(rpart)
library(rpart.plot)
dim(Heritage_RiskADeleted)
dtm <- rpart(RiskLevel~PrimaryConditionGroup,Heritage_RiskADeleted,method = "class")
dtm
rpart.plot(dtm)
```

### Question 6: IGNORE RISK LEVEL A.  Experiment with different schemes for quantizing risk level.  Do you notice a difference?	

## Below are the two rules generated for charlson index using Association Algorithm (arules package).

```{r charlson}
library(arules)
library(Matrix)
charlsonindex <-Heritage_RiskADeleted[,c(13,16)]
rules=apriori(charlsonindex,parameter = list(supp=0.1,conf=0.5,minlen=2))
rules=sort(rules,by="lift")
rules=sort(rules,by="lift")
inspect(rules)
```

## PrimaryconditionGroup using Association Algorithm (arules package).

```{r primary}
library(arules) 
library(Matrix)
primarycondition <-Heritage_RiskADeleted[,c(12,16)]
rules=apriori(primarycondition,parameter = list(supp=0.1,conf=0.5,minlen=2))
rules=sort(rules,by="lift")
inspect(rules)
```

##LengthOfStay using Association Algorithm (arules package).

```{r length}
library(arules)
library(Matrix)
length <-Heritage_RiskADeleted[,c(10,16)]
rules=apriori(length,parameter = list(supp=0.1,conf=0.5,minlen=2))
rules=sort(rules,by="lift")
inspect(rules)
```

###K-Means Clustering


```{r}
library(datasets)
library(dplyr)
library(VIM)
head(Heritage_RiskADeleted)
set.seed(20)
aggr(Heritage_RiskADeleted)
Heritage_RiskADeletedCluster <- kmeans(Heritage_RiskADeleted[, 1:2], 3, nstart = 20)
Heritage_RiskADeletedCluster
aggr(Heritage_RiskADeletedCluster$cluster)
table(Heritage_RiskADeletedCluster$cluster, Heritage_RiskADeleted$RiskLevel)
Heritage_RiskADeletedCluster$cluster <- as.factor(Heritage_RiskADeletedCluster$cluster)
```
