---
title: "Neural Network"
author: "Chaitali Sawant,Harshita Gadiraju and Shivani Agarwal"
date: "2/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Question 1
#before epoch1,Forward Propogation input x2 - data and weights
```{r}

x1 <- 0
x2 <- 1
h0 <- 1
h1x0 <- -.4
h1x1 <- .2
h1x2 <- .1
h2x0 <- -.2 
h2x1 <- .4
h2x2 <- -.1

x0 <- 1

o1h0 <- .1
o1h1 <- -.2
o1h2 <- .1
o2h0 <- .4
o2h1 <- -.1
o2h2 <- .1

t1 <- .1
t2 <- .9
n <- .1
a <- .9
```

##Hidden and output
```{r}
h1_f <- sum((x0*h1x0)+(x1*h1x1)+(x2*h1x2))
h1<- 1/(1+exp(-h1_f))
h1

h2_f <- sum((x0*h2x0)+(x1*h2x1)+(x2*h2x2))
h2<- 1/(1+exp(-h2_f))
h2

o1_f <- sum((x0*o1h0)+(h1*o1h1)+(h2*o1h2))
o1 <- 1/(1+exp(-o1_f))
o1

o2_f <- sum((x0*o2h0)+(h1*o2h1)+(h2*o2h2))
o2 <- 1/(1+exp(-o2_f))
o2
```

##Error Terms
```{r}
eo1 <-.5*(t1-o1)^2
eo2 <-.5*(t2-o2)^2
eo1
eo2
```

##Question 2
##backward propogation starts from output layer to hidden layer
```{r}
#sigmoid output weights
so1 <- o1*(1-o1)*(t1-o1)
so2 <- o2*(1-o2)*(t2-o2)

#new output weights
dw0 <- (n*so1*h0)+(a*0) #Delta weight for output 1
o1h0 <- o1h0+dw0

dw1 <- (n*so1*h1)+(a*0)
o1h1 <- o1h1+dw1

dw2 <- (n*so1*h2)+(a*0)
o1h2 <- o1h2+dw2

dw0 <- (n*so2*h0)+(a)*0
o2h0 <- o2h0+dw0

dw1 <- (n*so2*h1)+(a)*0
o2h1 <- o2h1+dw1

dw2 <- (n*so2*h2)+(a)*0
o2h2 <- o2h2+dw2

o1h0
o1h1
o1h2
o2h0
o2h1
o2h2
```

```{r}
##Presenting the data in a better way/form to understand it better using data.frame and putting the data into a new dataset  
bp_weightsoh <- as.data.frame(c(o1h0, o1h1, o1h2,o2h0,o2h1,o2h2))
colnames(bp_weightsoh) <- "o/p-h/n weights"
bp_weightsoh
```

##backward propogation from hidden layer to input layer
```{r}
##delta h node weights 
dh1 <- h1*(1-h1)*((so1*o1h1)+(so2*o2h1))
dh2 <- h2*(1-h2)*((so1*o1h2)+(so2*o2h2))

#new h node weights
dw0 <- (n*dh1*x0)+(a*0)
h1x0 <- h1x0+dw0
dw1 <- (n*dh1*x1)+(a*0)
h1x1 <- h1x1+dw0
dw2 <- (n*dh1*x2)+(a*0)
h1x2 <- h1x2+dw0

dw0 <- (n*dh1*x0)+(a*0)
h2x0 <- h2x0+dw0
dw1 <- (n*dh1*x1)+(a*0)
h2x1 <- h2x1+dw0
dw2 <- (n*dh1*x2)+(a*0)
h2x2 <- h2x2+dw0

h1x0
h1x1
h1x2
h2x0
h2x1
h2x2
```

```{r}
bp_weightshi <- as.data.frame(c(h1x0,h1x1,h1x2,h2x0,h2x1,h2x2))
colnames(bp_weightshi) <- "h/n-i/p weights"
bp_weightshi
```


##Question3 
#before epoch1,input 1 - data and weights (Forward Propogation)
```{r}
x1 <- 1
x2 <- 0
h1x0 <- -.4
h1x1 <- .2
h1x2 <- .1
h2x0 <- -.2 
h2x1 <- .4
h2x2 <- -.1

o1h0 <- .1
o1h1 <- -.2
o1h2 <- .1
o2h0 <- .4
o2h1 <- -.1
o2h2 <- .1

t1 <- .9
t2 <- .1
n <- .1
a <- .9
```

##Hidden and output
```{r}
h1_in <- sum((x1*h1x1)+(x2*h1x2)+(1*h1x0))
h1<- 1/(1+exp(-h1_in))
h1

h2_in <- sum((x1*h2x1)+(x2*h2x2)+(1*h2x0))
h2<- 1/(1+exp(-h2_in))
h2

o1_in <- sum((h1*o1h1)+(h2*o1h2)+(1*o1h0))
o1 <- 1/(1+exp(-o1_in))
o1

o2_in <- sum((h1*o2h1)+(h2*o2h2)+(1*o2h0))
o2 <- 1/(1+exp(-o2_in))
o2
```

##error term
```{r}
eo1 <-.5*(t1-o1)^2
eo2 <-.5*(t2-o2)^2
eo1
eo2
```

##backward propogation
```{r}
#delta output weights
so1 <- o1*(1-o1)*(t1-o1)
so2 <- o2*(1-o2)*(t2-o2)
so1
so2

#new output weights
dw0 <- (n*so1*1)+(a*0)
o1h0 <- o1h0+dw0

dw1 <- (n*so1*h1)+(a*0)
o1h1 <- o1h1+dw1

dw2 <- (n*so1*h2)+(a*0)
o1h2 <- o1h2+dw2


dw0 <- (n*so2*1)+(a)*0
o2h0 <- o2h0+dw0

dw1 <- (n*so2*h1)+(a)*0
o2h1 <- o2h1+dw1

dw2 <- (n*so2*h2)+(a)*0
o2h2 <- o2h2+dw2

o1h0
o1h1
o1h2
o2h0
o2h1
o2h2
```

```{r}
bp_input1_woh <- as.data.frame(c(o1h0, o1h1, o1h2,o2h0,o2h1,o2h2))
colnames(bp_input1_woh) <- "oh before epoch input 1 weights"
bp_input1_woh
```

```{r}
##delta h node weights   
dh1 <- h1*(1-h1)*((so1*o1h1)+(so2*o2h1))
dh2 <- h2*(1-h2)*((so1*o1h2)+(so2*o2h2))

#new h node weights
dw0 <- (n*dh1*1)+(a*0)
h1x0 <- h1x0+dw0
dw1 <- (n*dh1*x1)+(a*0)
h1x1 <- h1x1+dw0
dw2 <- (n*dh1*x2)+(a*0)
h1x2 <- h1x2+dw0

dw0 <- (n*dh1*1)+(a*0)
h2x0 <- h2x0+dw0
dw1 <- (n*dh1*x1)+(a*0)
h2x1 <- h2x1+dw0
dw2 <- (n*dh1*x2)+(a*0)
h2x2 <- h2x2+dw0

h1x0
h1x1
h1x2
h2x0
h2x1
h2x2
```

```{r}
bp_input1_whx <- as.data.frame(c(h1x0,h1x1,h1x2,h2x0,h2x1,h2x2))
colnames(bp_input1_whx) <- "hx before epoch input 1 weights"
bp_input1_whx
```

#before epoch1,input 2 - data and weights
```{r}
x1 <- 0
x2 <- 1
h1x0 <- -.4
h1x1 <- .2
h1x2 <- .1
h2x0 <- -.2 
h2x1 <- .4
h2x2 <- -.1

o1h0 <- .1
o1h1 <- -.2
o1h2 <- .1
o2h0 <- .4
o2h1 <- -.1
o2h2 <- .1

t1 <- .1
t2 <- .9
n <- .1
a <- .9
```

##Hidden and output
```{r}
h1_in <- sum((x1*h1x1)+(x2*h1x2)+(1*h1x0))
h1<- 1/(1+exp(-h1_in))
h1

h2_in <- sum((x1*h2x1)+(x2*h2x2)+(1*h2x0))
h2<- 1/(1+exp(-h2_in))
h2

o1_in <- sum((h1*o1h1)+(h2*o1h2)+(1*o1h0))
o1 <- 1/(1+exp(-o1_in))
o1

o2_in <- sum((h1*o2h1)+(h2*o2h2)+(1*o2h0))
o2 <- 1/(1+exp(-o2_in))
o2
```

##error term
```{r}
eo1 <-.5*(t1-o1)^2
eo2 <-.5*(t2-o2)^2
eo1
eo2
```

##backward propogation
```{r}
#delta output weights
so1 <- o1*(1-o1)*(t1-o1)
so2 <- o2*(1-o2)*(t2-o2)
so1
so2

#new output weights
dw0 <- (n*so1*1)+(a*0)
o1h0 <- o1h0+dw0

dw1 <- (n*so1*h1)+(a*0)
o1h1 <- o1h1+dw1

dw2 <- (n*so1*h2)+(a*0)
o1h2 <- o1h2+dw2


dw0 <- (n*so2*1)+(a)*0
o2h0 <- o2h0+dw0

dw1 <- (n*so2*h1)+(a)*0
o2h1 <- o2h1+dw1

dw2 <- (n*so2*h2)+(a)*0
o2h2 <- o2h2+dw2

o1h0
o1h1
o1h2
o2h0
o2h1
o2h2
```

```{r}
bp_input2_woh <- as.data.frame(c(o1h0, o1h1, o1h2,o2h0,o2h1,o2h2))
colnames(bp_input2_woh) <- "oh before epoch input 2 weights"
bp_input2_woh
```

```{r}
##delta h node weights 
dh1 <- h1*(1-h1)*((so1*o1h1)+(so2*o2h1))
dh2 <- h2*(1-h2)*((so1*o1h2)+(so2*o2h2))

#new h node weights
dw0 <- (n*dh1*1)+(a*0)
h1x0 <- h1x0+dw0
dw1 <- (n*dh1*x1)+(a*0)
h1x1 <- h1x1+dw0
dw2 <- (n*dh1*x2)+(a*0)
h1x2 <- h1x2+dw0

dw0 <- (n*dh1*1)+(a*0)
h2x0 <- h2x0+dw0
dw1 <- (n*dh1*x1)+(a*0)
h2x1 <- h2x1+dw0
dw2 <- (n*dh1*x2)+(a*0)
h2x2 <- h2x2+dw0

h1x0
h1x1
h1x2
h2x0
h2x1
h2x2
```

```{r}
bp_input2_whx <- as.data.frame(c(h1x0,h1x1,h1x2,h2x0,h2x1,h2x2))
colnames(bp_input2_whx) <- "hx before epoch input 2 weights"
bp_input2_whx
```

```{r}
cbind(bp_input1_woh,
      bp_input1_whx,
      bp_input2_woh,
      bp_input2_whx)
```

##new weights
```{r}
nw_oh <- (bp_input1_woh+bp_input2_woh)/2
nw_oh
nw_hx <- (bp_input1_whx+bp_input2_whx)/2
nw_hx
```


#after epoch1,input 1 - data and weights
```{r}
x1 <- 1
x2 <- 0

h1x0 <- nw_hx[1,1]
h1x1 <- nw_hx[2,1]
h1x2 <- nw_hx[3,1]
h2x0 <- nw_hx[4,1]
h2x1 <- nw_hx[5,1]
h2x2 <- nw_hx[6,1]

o1h0 <- nw_oh[1,1]
o1h1 <- nw_oh[2,1]
o1h2 <- nw_oh[3,1]
o2h0 <- nw_oh[4,1]
o2h1 <- nw_oh[5,1]
o2h2 <- nw_oh[6,1]

t1 <- .9
t2 <- .1
```

##Hidden and output
```{r}
h1_in <- sum((x1*h1x1)+(x2*h1x2)+(1*h1x0))
h1<- 1/(1+exp(-h1_in))
h1

h2_in <- sum((x1*h2x1)+(x2*h2x2)+(1*h2x0))
h2<- 1/(1+exp(-h2_in))
h2

o1_in <- sum((h1*o1h1)+(h2*o1h2)+(1*o1h0))
o1 <- 1/(1+exp(-o1_in))
o1

o2_in <- sum((h1*o2h1)+(h2*o2h2)+(1*o2h0))
o2 <- 1/(1+exp(-o2_in))
o2
```

##error
```{r}
Eo1 <-.5*(t1-o1)^2
Eo2 <-.5*(t2-o2)^2
Eo1
Eo2
```

##backward propogation
```{r}
#delta output weights
so1 <- o1*(1-o1)*(t1-o1)
so2 <- o2*(1-o2)*(t2-o2)
so1
so2

#new output weights
dw0 <- (n*so1*1)+(a*0)
o1h0 <- o1h0+dw0

dw1 <- (n*so1*h1)+(a*0)
o1h1 <- o1h1+dw1

dw2 <- (n*so1*h2)+(a*0)
o1h2 <- o1h2+dw2


dw0 <- (n*so2*1)+(a)*0
o2h0 <- o2h0+dw0

dw1 <- (n*so2*h1)+(a)*0
o2h1 <- o2h1+dw1

dw2 <- (n*so2*h2)+(a)*0
o2h2 <- o2h2+dw2

o1h0
o1h1
o1h2
o2h0
o2h1
o2h2
```

```{r}
bp_input1_woh <- as.data.frame(c(o1h0, o1h1, o1h2,o2h0,o2h1,o2h2))
colnames(bp_input1_woh) <- "oh after epoch 1 input 1 weights"
bp_input1_woh
```

```{r}
##delta h node weights   
dh1 <- h1*(1-h1)*((so1*o1h1)+(so2*o2h1))
dh2 <- h2*(1-h2)*((so1*o1h2)+(so2*o2h2))

#new h node weights
dw0 <- (n*dh1*1)+(a*0)
h1x0 <- h1x0+dw0
dw1 <- (n*dh1*x1)+(a*0)
h1x1 <- h1x1+dw0
dw2 <- (n*dh1*x2)+(a*0)
h1x2 <- h1x2+dw0

dw0 <- (n*dh1*1)+(a*0)
h2x0 <- h2x0+dw0
dw1 <- (n*dh1*x1)+(a*0)
h2x1 <- h2x1+dw0
dw2 <- (n*dh1*x2)+(a*0)
h2x2 <- h2x2+dw0

h1x0
h1x1
h1x2
h2x0
h2x1
h2x2
```

```{r}
bp_input1_whx <- as.data.frame(c(h1x0,h1x1,h1x2,h2x0,h2x1,h2x2))
colnames(bp_input1_whx) <- "hx after epoch 1 input 1 weights"
bp_input1_whx
```

#after epoch1,input 2 - data and weights
```{r}
x1 <- 0
x2 <- 1

h1x0 <- nw_hx[1,1]
h1x1 <- nw_hx[2,1]
h1x2 <- nw_hx[3,1]
h2x0 <- nw_hx[4,1]
h2x1 <- nw_hx[5,1]
h2x2 <- nw_hx[6,1]

o1h0 <- nw_oh[1,1]
o1h1 <- nw_oh[2,1]
o1h2 <- nw_oh[3,1]
o2h0 <- nw_oh[4,1]
o2h1 <- nw_oh[5,1]
o2h2 <- nw_oh[6,1]

t1 <- .1
t2 <- .9
```

##Hidden and output
```{r}
h1_in <- sum((x1*h1x1)+(x2*h1x2)+(1*h1x0))
h1<- 1/(1+exp(-h1_in))
h1

h2_in <- sum((x1*h2x1)+(x2*h2x2)+(1*h2x0))
h2<- 1/(1+exp(-h2_in))
h2

o1_in <- sum((h1*o1h1)+(h2*o1h2)+(1*o1h0))
o1 <- 1/(1+exp(-o1_in))
o1

o2_in <- sum((h1*o2h1)+(h2*o2h2)+(1*o2h0))
o2 <- 1/(1+exp(-o2_in))
o2
```

##error term
```{r}
eo1 <-.5*(t1-o1)^2
eo2 <-.5*(t2-o2)^2
eo1
eo2
```

##backward propogation
```{r}
#delta output weights
so1 <- o1*(1-o1)*(t1-o1)
so2 <- o2*(1-o2)*(t2-o2)
so1
so2

#new output weights
dw0 <- (n*so1*1)+(a*0)
o1h0 <- o1h0+dw0

dw1 <- (n*so1*h1)+(a*0)
o1h1 <- o1h1+dw1

dw2 <- (n*so1*h2)+(a*0)
o1h2 <- o1h2+dw2


dw0 <- (n*so2*1)+(a)*0
o2h0 <- o2h0+dw0

dw1 <- (n*so2*h1)+(a)*0
o2h1 <- o2h1+dw1

dw2 <- (n*so2*h2)+(a)*0
o2h2 <- o2h2+dw2

o1h0
o1h1
o1h2
o2h0
o2h1
o2h2
```

```{r}
bp_input2_woh <- as.data.frame(c(o1h0, o1h1, o1h2,o2h0,o2h1,o2h2))
colnames(bp_input2_woh) <- "oh after epoch1 input 2 weights"
bp_input2_woh
```

```{r}
##delta h node weights 
dh1 <- h1*(1-h1)*((so1*o1h1)+(so2*o2h1))
dh2 <- h2*(1-h2)*((so1*o1h2)+(so2*o2h2))

#new h node weights
dw0 <- (n*dh1*1)+(a*0)
h1x0 <- h1x0+dw0
dw1 <- (n*dh1*x1)+(a*0)
h1x1 <- h1x1+dw0
dw2 <- (n*dh1*x2)+(a*0)
h1x2 <- h1x2+dw0

dw0 <- (n*dh1*1)+(a*0)
h2x0 <- h2x0+dw0
dw1 <- (n*dh1*x1)+(a*0)
h2x1 <- h2x1+dw0
dw2 <- (n*dh1*x2)+(a*0)
h2x2 <- h2x2+dw0

h1x0
h1x1
h1x2
h2x0
h2x1
h2x2
```

```{r}
bp_input2_whx <- as.data.frame(c(h1x0,h1x1,h1x2,h2x0,h2x1,h2x2))
colnames(bp_input2_whx) <- "hx epoch1 input 2  weights"
bp_input2_whx
```

```{r}
cbind(bp_input1_woh,
      bp_input1_whx,
      bp_input2_woh,
      bp_input2_whx)
```

##new weights
```{r}
nw_oh <- (bp_input1_woh+bp_input2_woh)/2
nw_oh
nw_hx <- (bp_input1_whx+bp_input2_whx)/2
nw_hx
```


#after epoch2,input 1 - data and weights
```{r}
x1 <- 1
x2 <- 0

h1x0 <- nw_hx[1,1]
h1x1 <- nw_hx[2,1]
h1x2 <- nw_hx[3,1]
h2x0 <- nw_hx[4,1]
h2x1 <- nw_hx[5,1]
h2x2 <- nw_hx[6,1]

o1h0 <- nw_oh[1,1]
o1h1 <- nw_oh[2,1]
o1h2 <- nw_oh[3,1]
o2h0 <- nw_oh[4,1]
o2h1 <- nw_oh[5,1]
o2h2 <- nw_oh[6,1]

t1 <- .9
t2 <- .1
```

##Hidden and output
```{r}
h1_in <- sum((x1*h1x1)+(x2*h1x2)+(1*h1x0))
h1<- 1/(1+exp(-h1_in))
h1

h2_in <- sum((x1*h2x1)+(x2*h2x2)+(1*h2x0))
h2<- 1/(1+exp(-h2_in))
h2

o1_in <- sum((h1*o1h1)+(h2*o1h2)+(1*o1h0))
o1 <- 1/(1+exp(-o1_in))
o1

o2_in <- sum((h1*o2h1)+(h2*o2h2)+(1*o2h0))
o2 <- 1/(1+exp(-o2_in))
o2
```

##error term
```{r}
eo1 <-.5*(t1-o1)^2
eo2 <-.5*(t2-o2)^2
eo1
eo2
```

##backward propogation
```{r}
#delta output weights
so1 <- o1*(1-o1)*(t1-o1)
so2 <- o2*(1-o2)*(t2-o2)
so1
so2

#new output weights
dw0 <- (n*so1*1)+(a*0)
o1h0 <- o1h0+dw0

dw1 <- (n*so1*h1)+(a*0)
o1h1 <- o1h1+dw1

dw2 <- (n*so1*h2)+(a*0)
o1h2 <- o1h2+dw2


dw0 <- (n*so2*1)+(a)*0
o2h0 <- o2h0+dw0

dw1 <- (n*so2*h1)+(a)*0
o2h1 <- o2h1+dw1

dw2 <- (n*so2*h2)+(a)*0
o2h2 <- o2h2+dw2

o1h0
o1h1
o1h2
o2h0
o2h1
o2h2
```

```{r}
bp_input1_woh <- as.data.frame(c(o1h0, o1h1, o1h2,o2h0,o2h1,o2h2))
colnames(bp_input1_woh) <- "oh after epoch 2 input 1 weights"
bp_input1_woh
```

```{r}
##delta h node weights   
dh1 <- h1*(1-h1)*((so1*o1h1)+(so2*o2h1))
dh2 <- h2*(1-h2)*((so1*o1h2)+(so2*o2h2))

#new h node weights
dw0 <- (n*dh1*1)+(a*0)
h1x0 <- h1x0+dw0
dw1 <- (n*dh1*x1)+(a*0)
h1x1 <- h1x1+dw0
dw2 <- (n*dh1*x2)+(a*0)
h1x2 <- h1x2+dw0

dw0 <- (n*dh1*1)+(a*0)
h2x0 <- h2x0+dw0
dw1 <- (n*dh1*x1)+(a*0)
h2x1 <- h2x1+dw0
dw2 <- (n*dh1*x2)+(a*0)
h2x2 <- h2x2+dw0

h1x0
h1x1
h1x2
h2x0
h2x1
h2x2
```

```{r}
bp_input1_whx <- as.data.frame(c(h1x0,h1x1,h1x2,h2x0,h2x1,h2x2))
colnames(bp_input1_whx) <- "hx after epoch 2 input 1 weights"
bp_input1_whx
```

#after epoch2,input 2 - data and weights
```{r}
x1 <- 0
x2 <- 1

h1x0 <- nw_hx[1,1]
h1x1 <- nw_hx[2,1]
h1x2 <- nw_hx[3,1]
h2x0 <- nw_hx[4,1]
h2x1 <- nw_hx[5,1]
h2x2 <- nw_hx[6,1]

o1h0 <- nw_oh[1,1]
o1h1 <- nw_oh[2,1]
o1h2 <- nw_oh[3,1]
o2h0 <- nw_oh[4,1]
o2h1 <- nw_oh[5,1]
o2h2 <- nw_oh[6,1]

t1 <- .1
t2 <- .9
```

##Hidden and output
```{r}
h1_in <- sum((x1*h1x1)+(x2*h1x2)+(1*h1x0))
h1<- 1/(1+exp(-h1_in))
h1

h2_in <- sum((x1*h2x1)+(x2*h2x2)+(1*h2x0))
h2<- 1/(1+exp(-h2_in))
h2

o1_in <- sum((h1*o1h1)+(h2*o1h2)+(1*o1h0))
o1 <- 1/(1+exp(-o1_in))
o1

o2_in <- sum((h1*o2h1)+(h2*o2h2)+(1*o2h0))
o2 <- 1/(1+exp(-o2_in))
o2
```

##error term
```{r}
eo1 <-.5*(t1-o1)^2
eo2 <-.5*(t2-o2)^2
eo1
eo2
```

##backward propogation
```{r}
#delta output weights
so1 <- o1*(1-o1)*(t1-o1)
so2 <- o2*(1-o2)*(t2-o2)
so1
so2

#new output weights
dw0 <- (n*so1*1)+(a*0)
o1h0 <- o1h0+dw0

dw1 <- (n*so1*h1)+(a*0)
o1h1 <- o1h1+dw1

dw2 <- (n*so1*h2)+(a*0)
o1h2 <- o1h2+dw2


dw0 <- (n*so2*1)+(a)*0
o2h0 <- o2h0+dw0

dw1 <- (n*so2*h1)+(a)*0
o2h1 <- o2h1+dw1

dw2 <- (n*so2*h2)+(a)*0
o2h2 <- o2h2+dw2

o1h0
o1h1
o1h2
o2h0
o2h1
o2h2
```

```{r}
bp_input2_woh <- as.data.frame(c(o1h0, o1h1, o1h2,o2h0,o2h1,o2h2))
colnames(bp_input2_woh) <- "oh input 2 after epoch 2 weights"
bp_input2_woh
```

```{r}
##delta h node weights 
dh1 <- h1*(1-h1)*((so1*o1h1)+(so2*o2h1))
dh2 <- h2*(1-h2)*((so1*o1h2)+(so2*o2h2))

#new h node weights
dw0 <- (n*dh1*1)+(a*0)
h1x0 <- h1x0+dw0
dw1 <- (n*dh1*x1)+(a*0)
h1x1 <- h1x1+dw0
dw2 <- (n*dh1*x2)+(a*0)
h1x2 <- h1x2+dw0

dw0 <- (n*dh1*1)+(a*0)
h2x0 <- h2x0+dw0
dw1 <- (n*dh1*x1)+(a*0)
h2x1 <- h2x1+dw0
dw2 <- (n*dh1*x2)+(a*0)
h2x2 <- h2x2+dw0

h1x0
h1x1
h1x2
h2x0
h2x1
h2x2
```

```{r}
bp_input2_whx <- as.data.frame(c(h1x0,h1x1,h1x2,h2x0,h2x1,h2x2))
colnames(bp_input2_whx) <- "hx input 2 after epoch 2 weights"
bp_input2_whx
```

```{r}
cbind(bp_input1_woh,
      bp_input1_whx,
      bp_input2_woh,
      bp_input2_whx)
```

##new weights
```{r}
nw_oh <- (bp_input1_woh+bp_input2_woh)/2
nw_oh
nw_hx <- (bp_input1_whx+bp_input2_whx)/2
nw_hx
```

